%!TEX root = /Users/kevin/SkyDrive/KTH Work/Period 4 2014/GNSS/Labs/L4 - Kalman filtering/main.tex


\section{Analysis and Discussion} % (fold)
\label{sec:analysis_and_discussion}
% In this part you should discuss your results by, for example, considering the following questions:
\begin{itemize}
	\item What happens if we change the values of 
	\begin{itemize}
		\item[a)] PSD?
		
		The value of the PSD changes the covariance matrix, $\+Q_k$, which then affects the random accelerations of the vehicle measurements.  Increasing the PSD would increase the standard deviations of our filter and smoothing results.
		\item[b)] Standard deviations of measurements?
		
		Changing the standard deviations of the measurements increases the standard deviations of the filtered results but doesn't affect the smoothing results.
		\item[c)] Standard deviations of initial state variables?
		
		Increasing the standard deviations of the initial state variables only affects our ability to calculate the precise location of the car at that time.  The more measurements we have, the less important the initial state becomes.
	\end{itemize}

	\item Can we draw any conclusion/implications from the results?  
	
	We can conclude that the smoothed coordinates are a better approximation to the true values than the filtered coordinates.
	\item Are results reliable and accurate?
	
	I believe the results are reliable and accurate because the standard deviations dropped when the coordinates were smoothed and the state vector was a better approximation of the true values. Figures~\ref{fig:Figures_diffPlots} and \ref{fig:Figures_diffPlotsVelocity} shows that the smoothed values are closer to $(0,0)$ than the filtered values.

\end{itemize}

% section analysis_and_discussion (end)
